Combinatorial Mixture Models for Single-Cell Assays with Application to Vaccine Studies

### 2012-07-30 MIMOSA.tex
Updated the grant number.

\section*{Acknowledgments}
GF and RG acknowledge funding from National Institute of Health grants R01 EB008400 and U01 AI068635-01, and a Bill \& Melinda Gates Foundation grant OPP38744 \footnote{Change this number later}. 
%\section{Data Import, Preprocessing, and Gating}
%The ICS assay data was imported into R from the original flowJo workspaces (version 6, TreeStar Inc, Ashland, OR)  using the BioConductor tool, \textit{flowWorkspace} (v 1.1.6) and ncdfFlow (v 1.1.4). Data were preprocessed using the flowJo-defined compensation matrices and data transformations extracted from the workspace file, and gated using methods from the flowCore package (v 1.19.2) to extract counts of cytokine positive and negative T-cells for each sample and stimulation~\cite{Hahne:2009vv}.

>>>>

\section*{Acknowledgments}
GF and RG acknowledge funding from National Institute of Health grants R01 EB008400 and U01 AI068635-01, and a Bill \& Melinda Gates Foundation grant OPP1032317. 
%\section{Data Import, Preprocessing, and Gating}
%The ICS assay data was imported into R from the original flowJo workspaces (version 6, TreeStar Inc, Ashland, OR)  using the BioConductor tool, \textit{flowWorkspace} (v 1.1.6) and ncdfFlow (v 1.1.4). Data were preprocessed using the flowJo-defined compensation matrices and data transformations extracted from the workspace file, and gated using methods from the flowCore package (v 1.19.2) to extract counts of cytokine positive and negative T-cells for each sample and stimulation~\cite{Hahne:2009vv}.
